Adaptive Sequential Model Selection

### 2015-05-12 paper.tex
added section on computation, along with theorem about forward stepwise constraints

@@

\WFcomment{Should we compute the FWER and FDR only conditional on screening? Strong / Forward / Simple should all be correct given screening since they condition on $p_{[k_0-1]}$.}

>>>>

\section{Computation}

As usual, we have reduced computation of the $p$-value at step $k$ to a sampling problem. Whatever our test statistic at step $k$, we must compute its distribution under the null model $M_{k-1}$.

Happily, the polytope to condition on has only $2p$ constraints in forward stepwise regression, as we see next.

\begin{theorem}
  Assume the model path $M_{[d]}$ is obtained by forward stepwise 
  linear regression. Then, for a candidate active set $E$ of size $k$, 
  the set $A = \{E_k = E, \;X_E'Y = u\}$ is characterized 
  exactly by the constraints $X_E'Y=u$ and
  \[
  v_j^-(E,u) < X_j'Y < v_j^+(E,u), \quad\forall j \notin E,
  \]
  for $v_j^-$ and $v_j^+$ given explicitly in
  Equations~(\ref{eq:vMinus_FS}--\ref{eq:vPlus_FS}).
  Thus, $A$ corresponds exactly to 
  a set with $2(p-k)$ linear inequality constraints and $k$
  linear equality constraints on $Y$.
\end{theorem}

\begin{proof}
  At stage $i < k$, the next variable to enter is the one with maximal correlation with the residual vector; i.e.
  \[
  j_{i+1} = \argmax_{j \notin E_i} 
  \frac{\left| X_j ' (Y - X_{E_i}\hat\beta^i) \right|}
  {\|\proj_{E_i}^\perp X_j\|}
  \]
  The crucial observation is that, 
  once we know the $k$th active set 
  $E_k$ and its sufficient statistics
  $X_{E_k}'Y$, we know the entire 
  path of fitted models up to step $k$.
  On the set $\{E_k=E\}$, all of the quantities 
  $j_{i+1}$, $E_i$, $\hat\beta^i$, and $\proj_{E_i}^\perp$
  depend only on $X_E'Y$. For brevity, write
  \[
  C_i^* = \max_{j \notin E_i} 
  \frac{\left| X_j ' (Y - X_{E_i}\hat\beta^i) \right|}
  {\|\proj_{E_i}^\perp X_j\|}.
  \]
  On $A$, $C_i^*$ is attained at $j=j_{i+1}$, the $i$th 
  variable added.

  If $X_E'Y$ is fixed at $u$, and $j \notin E$, then the condition for 
  $X_j$ {\em not} to enter at step $i+1 < k$ is
  \[
  \frac{\left| X_j' (Y - X_{E_i}\hat\beta^i) \right|}
  {\|\proj_{E_i}^\perp X_j\|} 
  \leq C_i^*,
  \]
  or equivalently,
  \begin{equation}\label{eq:noEnterBounds_FS}
    X_j' X_{E_i}\hat\beta^i -
    C_i^*\|\proj_{E_{i}}^\perp X_{j}\|
    \;\;\;\leq\;\;\;
    X_j'Y
    \;\;\;\leq\;\;\;
    X_j' X_{E_i}\hat\beta^i +
    C_i^*\|\proj_{E_{i}}^\perp X_{j}\|, 
  \end{equation}
  so the set $A$ is equivalent to 
  Equation~\eqref{eq:noEnterBounds_FS} holding
  for every $i < k$ and $j \notin E$. Nominally, this gives $2k(p-k)$
  linear inequality constraints to satisfy, but most of them are
  non-binding. On $A$, the upper and lower bounds
  in~\eqref{eq:noEnterBounds_FS}
  are all known functions of $E$ and $u$, so we can set
  \begin{align}\label{eq:vMinus_FS}
    v_j^-(E,u) &= \max_{0 \leq i < k} \;\;X_j' X_{E_i}\hat\beta^i -
    C_i^*\|\proj_{E_{i}}^\perp X_{j}\| \\
    \label{eq:vPlus_FS}
    v_j^+(E,u) &= \min_{0 \leq i < k} \;\;X_j' X_{E_i}\hat\beta^i +
    C_i^*\|\proj_{E_{i}}^\perp X_{j}\|.
  \end{align}  
\end{proof}

As we see below, a similar result holds for the LASSO ever-active path. In fact, it holds for a much larger class of $\ell_1$ regularized exponential family models including the graphical LASSO, group LASSO, and...
\WFcomment{Fill in this proof.}

@@

\WFcomment{Should we compute the FWER and FDR only conditional on screening? Strong / Forward / Basic should all be correct given screening since they condition on $p_{[k_0-1]}$.}
